% !TEX root = ../thesis-example.tex
%
\chapter{Conclusions}
\label{sec:conclusions}

\section{Limitations}

\begin{itemize}
	\item Training a 3D based model is expensive so we could only use pretrained things
	\item Face detection is not addressed specifically in tasks so we used pedestrian and saw the performance
	\item Real-time processing is not yet feasible(I should measure the inference time)
\end{itemize}

\par The 3D AI-based Object Detection and general pointcloud processing python ecosystem is not that mature yet.
There are great tools that are either still at an early research phase or not properly maintained. This makes them unsuitable for software in production environments.
\href{https://github.com/vinits5/learning3d}{Learning3D} is a python project that implements some basic models such as PointNet and DGCNN, providing pretrained weights.
The problem is that there are no official releases on package registries, making integration with existing work more difficult.

% also not agreeing on pytorch versions
% also openmmlab just stopped maintaining stuff
% not that general object detection classes
\href{https://github.com/isl-org/Open3D/}{Open3D}

More specifically, python versions are outdated, only specific versions of packages are supported.
Pretrained and actually useful models are rare in contrast to 2D where for example opencv offers
out of the box several object and face detection modules.

\par Face detection as a specific task is not that popular in Point cloud related settings. Mostly pedestrians in an outdoor setting are actually the target of the latest models. There has been more focus in face recognition tasks as point clouds can provide richer features of a face than the two-dimensional equivalent and can therefore improve the effectiveness of face recognition systems.

\par Most of the attention is on traffic settings, other use cases remain mostly unexplored e.g. indoors 3D cameras.
In \cite{wang_voxel-rcnn-complex_2022} the authors improve upon an existing model to make it more suitable for complex traffic conditions.
\section{Discussion}

\section{Future Work}
